\documentclass[]{report}

\voffset=-1.5cm
\oddsidemargin=0.0cm
\textwidth = 480pt

\usepackage{framed}
\usepackage{subfiles}
\usepackage{graphics}
\usepackage{newlfont}
\usepackage{eurosym}
\usepackage{amsmath,amsthm,amsfonts}
\usepackage{amsmath}
\usepackage{color}
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\begin{document}

%======================================================== %

\subsubsection{Question 4}
The following data give the marks of 10 students in a test (out of 20 marks). Calculate
i) the median    ii) the mean     iii) the range    iv) the standard deviation v) The Inter-Quartile Range

12, 17, 7, 11, 18, 6, 14, 15, 11, 9.
\subsection{Question 1}

Consider the following \emph{sample} of numbers:
\begin{center}
\begin{tabular}{|cccccccccc|}
\hline
&&&&&&&&&\\[-0.4cm]
2 & 4 & 2 & 1 & 5 & 3 & 0 & 4 & 1 & 8 \\
\hline
\end{tabular}
\end{center}
\begin{enumerate}[a)]\itemsep0.3cm
\item What is the value of $n$\,?
\item Calculate the mean and use the appropriate symbol.
\item What is the symbol for the population mean? What is its value?
\item Calculate $Q_2$ (hint: need to order the data first).
\item Construct a frequency table with 3 classes (let zero be the first breakpoint).
\item Draw the corresponding histogram.
\end{enumerate}





\section{Question 2}

25 individuals were asked how long their laptop lasts on a full charge. The recorded times (measured in hours) are as follows:\\
{\footnotesize(we saw this dataset before - lecture 1, Q5)}
\begin{center}
\begin{tabular}{|cccccccccc|}
\hline
&&&&&&&&&\\[-0.4cm]
2.2 & 0.4 & 4.2 & 12.9 & 1.5 & 3.0 & 5.7  & 0.7 & 1.0 & 3.3 \\
0.2 & 0.2 & 5.6 &  1.6 & 3.0 & 0.1 & 14.3 & 3.4 & 0.9 & 6.1 \\
1.4 & 1.0 & 0.7 & 5.4  & 2.3 &&&&&\\
\hline
\end{tabular}
\end{center}
\begin{enumerate}[a)]\itemsep0.3cm
\item Calculate $\bar x$.
\item Calculate $s$.
\item What is the symbol for the population standard deviation? What is our best estimate of this?
\item What is the value of $\mu$?
\item What is the value of $\hat p$?
\end{enumerate}


\end{document}

