\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{enumerate}
\usepackage{multicol}
\usepackage{subfigure}
\usepackage{fancyhdr}
\usepackage{listings}
\usepackage{framed}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{chngpage}
%\usepackage{bigints}

\usepackage{vmargin}
% left top textwidth textheight headheight
% headsep footheight footskip
\setmargins{2.0cm}{2.5cm}{16 cm}{22cm}{0.5cm}{0cm}{1cm}{1cm}
\renewcommand{\baselinestretch}{1.3}

\setcounter{MaxMatrixCols}{10}
\begin{document}
\large \noindent A fruit grower wishes to test a new spray that a manufacturer claims will
reduce the amount of fruit lost due to damage by a certain insect. To test
the claim, the grower sprays 150 trees with the new spray and 120 other
trees with the standard spray. The yield of fruit was measured, in kg, for
each tree. Summary statistics were as follows. You may assume equal variance for the populations.

\begin{center}
\begin{tabular}{|c|c|c|} \hline 
                       & New spray & Standard spray\\ \hline 
Sample yield per tree  & 280       & 255\\ \hline 
Sample variance        & 650      & 640\\ \hline 
\end{tabular}
\end{center}
\begin{enumerate}[(a)]
\item Construct a 95\% confidence interval for the difference between the mean yields for the two sprays and interpret your findings. 
\item Test the hypothesis that the new spray is effective in reducing damage. Clearly state your null and alternative hypotheses and your conclusion. Use a significance level of 5\%.
\end{enumerate}



\begin{framed}
The general structure of a confidence interval is as follows:

\[ \mbox{Point Estimate}  \pm \left[ \mbox{Quantile} \times \mbox{Standard Error} \right] \]


\begin{itemize}
\item Point Estimate: estimate for population parameter of interest, i.e. sample mean, sample proportion.
\item Quantile: a value from a probability distribution that scales the intervals according to the specified confidence level.
\item Standard Error: measures the dispersion of the sampling distribution for a given sample size $n$.
\end{itemize}
\end{framed}

\subsection*{Part (a)}

\begin{itemize}
\item
\item
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\subsection*{Part (b)}

\begin{itemize}
\item
\item
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\subsection*{Part (c)}

\begin{itemize}
\item
\item
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
