\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{framed}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode"CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 201113:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{StatsResource} \rhead{Inference Procedures} \chead{Confidence Intervals} %\input{tcilatex}

\begin{document}
\large 

\section*{Confidence Intervals - Worked Example}
A press release for a broadband provider stated that $90\%$ percent of customers are very satisfied
with the standard of service. To test this claim, the local chamber of commerce surveyed 110 randomly selected customers. Among the sampled customers, 89 stated that they are very satisfied.


%Test the hypothesis that $90\%$ of all customers are very satisfied with their service. You may assume a significance level of 5\%.



\begin{itemize}
\item[(i)]  Compute the appropriate value for the standard error for a confidence interval.
\item[(ii)] Compute the 95\% confidence interval for $\pi$, the true proportion.
%\item[iii] (2 marks) For the test statistic, determine the corresponding p-value.
\item[(iii)] What is your conclusion for this claim made by the press release? Justify your answer.
\end{itemize}
%--------------------------------- %

\subsection*{Confidence Intervals}
General Structure of a confidence interval

\[ \mbox{Point Estimate} \pm \left( \mbox{Quantile} \times \mbox{Standard Error} \right) \]

\subsection*{Solution}

\begin{itemize}
\item Point estimate = 0.81 (89/110)
\item Large Sample : 95\% Quantile = 1.96
\item Standard Error 
\[S.E.(\hat{p}) =  \sqrt{  \frac{\hat{p} \times (1-\hat{p})}{n} }\]
\[S.E.(\hat{p}) = \sqrt{\frac{0.81 \times 0.19}{110}} = \sqrt{0.001411}\]
\[S.E.(\hat{p}) = 0.0374\]
\item Margin of Error = $1.96 \times 0.0374$ = 0.07345
\item Answer : (0.81 - 0.07345, 0.81 + 0.07344) =  (0.7356,0.8825)
\item 0.90 not in 95\% confidence interval - the claim not supported on this evidence. 
\end{itemize}
\newpage
BLANK
\end{document}
