
\documentclass[a4paper12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{enumerate}
\usepackage{multicol}
\usepackage{subfigure}
\usepackage{fancyhdr}
\usepackage{listings}
\usepackage{framed}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{chngpage}
%\usepackage{bigints}

\usepackage{vmargin}
% left top textwidth textheight headheight
% headsep footheight footskip
\setmargins{2.0cm}{2.5cm}{16 cm}{22cm}{0.5cm}{0cm}{1cm}{1cm}
\renewcommand{\baselinestretch}{1.3}

\setcounter{MaxMatrixCols}{10}

\begin{document}
\large 


%%- http://webpages.iust.ac.ir/matashbar/teaching/schaum_probability.pdf

%%-- PAge 287
%%-- 9.13

\noindent An air freight terminal has four loading docks on the main concourse. Any aircraft which arrive 
when all docks are full are diverted to docks on the back concourse. The average aircraft arrival

rate is 3 aircraft per hour. 

The average service time per aircraft is 2 hours on the main concourse and 3 hours on the back concourse. 
\begin{enumerate}[(a)]
    \item Find the percentage of the arriving aircraft that are diverted to the back concourse. 
    \item If a holding area which can accommodate up to 8 aircraft is added to the main concourse, 
find the percentage of the arriving aircraft that are diverted to the back concourse and the 
expected delay time awaiting service. 
\end{enumerate}

\subsection*{Solution}

\begin{itemize}
    \item The service system at the main concourse can be modeled as an \textbf{M/M/s/s} queueing system with $s = 4$, 
1 = 3, p = 3, and 1/p = 6. 
\item The percentage of the arriving aircraft that are diverted to the back concourse is 
\[100 x P(al1 docks on the main concourse are full) \]
    \item From Eq. (9.64), 
64/4 ! P(al1 docks on the main concourse are full) = p, = 7 -- 54 P 0.47 115 C 9 n=O 
    \item Thus, the percentage of the arriving aircraft that are diverted to the back concourse is about 47 
percent. 
    \item With the addition of a holding area for 8 aircraft, the service system at the main concourse can now be 
modeled as an \textbf{M/M/s/K} queueing system with $s = 4$, $K = 12$, and p = A/(sp) = 1.5. 
\item NOW, from Eqs. 
(9.35) and (9.36), 
    \item Thus, about 33.2 percent of the arriving aircraft will still be diverted to the back concourse. 
    \item Next, from Eq. (9.37), the average number of aircraft in the queue is 
    \item Then, from Eq. (9.40), the expected delay time waiting for service is 
W, = Lq = 6'0565 P 3.022 hours 
1 - ) 3(1 - 0.332) 
    \item Note that when the 2-hour service time is added, the total expected processing time at the main 
concourse will be 5.022 hours compared to the 3-hour service time at the back concourse. 
\end{itemize}


\end{document}