\documentclass[]{article}

\usepackage{amsmath}
\usepackage{amssymb}
%opening
\title{}
\author{}

\begin{document}

\maketitle


\section*{Question 1}

\subsection*{Part A}
Important Information
\begin{itemize}
\item Asked to compute $P(D) $: Defective
\item Suppliers: Company A : $P(A) = 0.70$ / Company B : $P(B) = 0.30$
\item Conditional Probability formule
\[ P(A|B) = \frac{P(A \mbox{ and } B  )}{P(B)}\]
Re-arranged
\[P(A \mbox{ and } B  ) = P(A|B)\times P(B)\]
\item $P(D|A) = 0.02$
\item $P(D|B) = 0.03$
\end{itemize}
\textbf{Using Total Probability Law}
\[P(D) = P(D \mbox{ and } A) + P(D \mbox{ and } B  )\]

\[P(D) = P(D|A)\times P(A) + P(D|B)\times P(B)\]

\[P(D) = 0.02 \times 0.70 +  0.03 \times 0.30  = 0.014 + 0.0009 = 0.023\]

\textbf{Part 2}
\[P(A|D)  = \frac{P(D|A)\times P(A)}{P(D)}  = \frac{0.02 \times 0.70}{0.023} =  0.6086\]

%------------------------- %
\subsection*{Part B}
\begin{itemize}
\item Mean
\[\bar{x} =  \frac{4 + 18 + 2 + 7 +18 + 3  +4
}{7} =56/7 = 8 \]
\item Median\\
Firstly: put the data set in order.\\
Median is middle value (4)\\
\item Variance
\[s^2 = \frac{\sum (x-\bar{x})^2}{n-1}\]
Ans = $\frac{294}{6} = 49$
\item Standard deviation is the square root of the variance. $s=7$
\end{itemize}
\subsection*{Part C : Discrete RVs}
\begin{itemize}
\item Find $k$\\
$P(X=2) = 0.25$. The sum of the probabilities must sum up to 1.

\item $E(X) = \sum x_i p(x_i)$ = 9.5

\[\sum x_i p(x_i) = (2\times 0.25) + (5 \times 0.25) + (10 \times 0.15) + (15 \times 0.25) + (25 \times 0.10) \]



\item $E(X^2) = \sum x^2_i p(x_i)$

\[\sum x_i p(x_i) = (4\times 0.25) + (25 \times 0.25) + (100 \times 0.15) + (225 \times 0.25) + (625 \times 0.10) \]


$E(X^2) = 141$

\item $V(X) = E(X^2) - E(X)^2 = 141-9.5^2 = 50.75$
\end{itemize}

\subsection*{Part D : Sampling without replacement}

\begin{itemize}
\item P(At least one is white) = 1-P(neither is white)
\item $1- \left[(4/10)\times (3/9)\right]  = 78/90 = 0.8666$
\item P(Exactly one) - disjoint events
\item probability is sum of components
\item First is white $4/10 \times 6/9 =20/90$
\item Second is white $6/10 \times 4/9 =20/90 $also
\item P(Exactly One white )=40/90
\end{itemize}

\subsection*{Part E : Probability Laws}
\begin{itemize}
\item $P(A \cap B)  = P(A) \times P(B) = 0.5\times 0.4 = 0.2 $
\item $P(A \cup B)  = P(A) + P(B) - P(A \cap B) = 0.7$
\end{itemize}

%----------------------------------------------- %
\newpage
\section*{Question 2}
\subsection*{Part A : Poisson Dsitribution}
Parameter: Poisson Mean m=3\\
Use statistical tables : Murdoch Barnes 2\\
\begin{itemize}
\item From tables $P(X \geq 2)$ = 0.8009
\item From tables $P(X = 0) = 1-P(X \geq 1)$ = 1-0.9502 = 0.0498
\item From tables $P(X = 1) = P(X \geq 1) - P(X \geq 2) $ = 0.9502 - 0.8009 = 0.1493
\item Poisson Mean $m=3$  and Poisson Standard Deviation $m=3$
\end{itemize}
\subsection*{Part B : Binomial Distribution}
n=100, p=0.05
\begin{itemize}
\item from tables: $P(X=5) = P(X \geq 5) - P(X \geq 6) = 0.5640 - 0.3840 = 0.18$
\item from tables: $P(X \geq 10) = 0.0282$
\item from tables: $P(X \leq 12) = 1-P(X\geq 13) = 1- 0.0015 = 0.9985$
\end{itemize}
\subsection*{Part C : Exponential Distribution}
Exponential Mean =10\\
Rate Parameter Lambda ($\lambda$) =1/10\\
Therefore $P(X \geq k ) = exp(-k/10)$
\begin{itemize}
\item $P(X \geq 10 ) = exp(-10/10) = exp(-1) = 0.3678$
\item $P(X \geq 10 ) = exp(-20/10) = exp(-2) = 0.1353$
\end{itemize}

\subsection*{Part D : Poisson Approximation}
\begin{itemize}
\item Bin(n,p)
\item Poisson(m)
\item Appropropriate when n is greater than 50 and p is less than 0.05.
\item Let $m = np$ and compute as poisson distribution.
\item For large values of n and really small vaues of p, Poisson Approximation is much simpler computationally, with negligible error.
\end{itemize}
%----------------------------------------------- %
\newpage
\section*{Question 3}
\subsection*{Part A : Normal Distribution}
Parameter Mean $\mu =1000$ Standard Deviation $\sigma=50$
Normal Distribution

\[ X \sim N(\mu=1000,\sigma^2=50^2)\]

\begin{itemize}
\item Compute $P(X \geq 975)$
\item Zscore
\[ z = frac{975 - 1000}{50} = -25/50 = -0.5\]
\item using Z identity and Symmetry rule
$P(X \geq 975)$ = $P(Z \geq -0.5)$ = $P(Z \leq -0.5)$ =  0.6914
\item Values derived from statistical tables
\end{itemize}

\begin{itemize}
\item Compute $P(X \leq 950)$
\item Zscore
\[ z = frac{950 - 1000}{50} = -50/50 = -1\]
\item using Z identity and Symmetry rule
$P(X \leq 950)$ = $P(Z \leq -0.1)$ = $P(Z \geq 1)$ = 0.8413
\item Values derived from statistical tables
\end{itemize}

\subsection*{Part B : Short Theory Definitions}
From Notes.
\subsection*{Part C : Confidence interval}

\begin{itemize}
\item Point estimate = 0.81 (89/110)
\item Large Sample : 95\% Quantile = 1.96
\item Standard Error 
\[S.E.(\hat{p}) =  \sqrt{  \frac{\hat{p} \times (1-\hat{p})}{n} }\]
\[S.E.(\hat{p}) = \sqrt{\frac{0.81 \times 0.19}{110}} = \sqrt{0.001411}\]
\[S.E.(\hat{p}) = 0.0374\]
\item Margin of Error = $1.96 \times 0.0374$ = 0.07345
\item Answer : (0.81 - 0.07345, 0.81 + 0.07344) =  (0.7356,0.8825)
\item 0.90 in interval - can contradict claim.
\end{itemize}
\subsection*{Part D : Shapiro Wilk Test}
Null: Data Set is normally distributed\\
Alt : Data set is not normally distributed\\
conclusion : Large p-value. Fail to reject null.
\subsection*{Part E : Normal Probability Plot}
\begin{itemize}
\item If the points on the plot follow the trendline, then the data set can be assumed to be normally distributed. (Marks for sketch, counter example etc)
\item Data is normally distributed.
\end{itemize}
%----------------------------------------------- %
\newpage
\section*{Question 4}

\subsection*{Accuracy, predicion recall}
Accuracy, Precision and recall are defined as
\[\mbox{Accuracy}=\frac{tp+tn}{tp+tn+fp+fn} \]
\[\mbox{Precision}=\frac{tp}{tp+fp} \] 
\[\mbox{Recall}=\frac{tp}{tp+fn} \]

The F measure is computed as
\[F = 2 \cdot \frac{\mathrm{precision} \cdot \mathrm{recall}}{ \mathrm{precision} + \mathrm{recall}}\]
%\subsection*{Questions}
\begin{center}
\begin{tabular}{|c|c|c|}
\hline  & \phantom{spa}Predict Negative\phantom{spa} & \phantom{spa}Predict Positive\phantom{spa} \\ 
\hline\phantom{spa} Observed Negative \phantom{spa}&	9530	&	10	\\ 
\hline \phantom{spa}Observed Positive\phantom{spa} & 	300	&	160	\\ 
\hline 
\end{tabular} 
\end{center}
Accuracy, Precision and recall are defined as
\[\mbox{Accuracy}=\frac{tp+tn}{tp+tn+fp+fn} = 0.9790 \]
\[\mbox{Precision}=\frac{tp}{tp+fp} = \frac{160}{170} = 0.9411\] 
\[\mbox{Recall}=\frac{tp}{tp+fn} =\frac{300}{460} = 0.6521 \]

The F measure is computed as
\[F = 2 \cdot \frac{\mathrm{precision} \cdot \mathrm{recall}}{ \mathrm{precision} + \mathrm{recall}}\]

\[ = \frac{2 \times 0.6521 \times 0.9411}{0.6521 + 0.9411}\]

\subsection*{Two sample mean}
\begin{itemize}
\item Hypotheses (brief written description required)
\[ H_0 :  \mu_1 = \mu_2\]
\[ H_1 :  \mu_1 \neq \mu_2\]
\item 
\item point estimate:  diffference in means (950-910=) 40 marks
\item Standard Error (from formulae)
\[\sqrt{\frac{s^2_1}{n_1} + \frac{s^2_2}{n_2} }\]
\item Critical Value = 1.96 (Large Sample.)
\end{itemize}

\subsection*{Two Sample proportion}
\begin{itemize}
\item Hypotheses (brief written description required)
\[ H_0 :  \pi_1 = \pi_2\]
\[ H_1 :  \pi_1 \neq \pi_2\]
\item point estimate:  diffference in proportions
\item Critical Value = 1.96 (Large Sample.)
\end{itemize}
%----------------------------------------------- %
\newpage
\section*{Question 5}
\subsection*{Part A : Huffman Coding}

\subsection*{Part B : Binary Channels}

\subsection*{Part C : Rate of Information}
\[R = rH(X)\]
\begin{itemize}
\item $H(X) = - \sum \limits^{16}_{i=1} {1\over 16} \mbox{log}_2{1\over 16}$ \bigskip

\item i.e. $H(X) = [ -{1\over 16} \mbox{log}_2{1\over 16} ] + [- {1\over 16} \mbox{log}_2{1\over 16} ] \ldots [ -{1\over 16} \mbox{log}_2{1\over 16}) ] $ \bigskip
\item Sixteen identical terms. Compute one and multiply by 16.

\[ H(X) = 16 \times [ -{1\over 16} \mbox{log}_2{1\over 16} ]  = -\mbox{log}_2{1\over 16} = -(-4) = 4\] \bigskip
\item $H(X)= 4$ b
\item $r =  2(10^6)(32) = 64(10^6)$ elements/sec \bigskip

\item $R = rH(X) = 64(10^6)(4) = 256(l0^6) \mbox{ b/sec } = 256 \mbox{ Mb/sec }$ \bigskip
\end{itemize}
\end{document}
