\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{multicol}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{framed}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode"CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 201113:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{MathsResource} \chead{Introduction to Calculus} \rhead{Curve Sketching} %\input{tcilatex}
\begin{document}



\begin{enumerate}

	\item Find the x-intercepts and the y-intercept of the following function

\begin{multicols}{2}

\[\mbox{(a)} f(x) = x^2 - 7x + 12  \]	

\[\mbox{(b)}  f(x) = x^2 - 9x + 14  \]

\[\mbox{(c)}  f(x) = x^2 - 8x + 12 \]

\[\mbox{(d)}  f(x) = x^2 + 6x + 8  \]

\end{multicols}
% - \[ f(x) = x^2 - 8x + 7  \]

%% - Horizontal and Vertical Asymptotes
%% - http://media.wix.com/ugd/70b98b_39a909a40ea3098062c0bebfb4304ed6.pdf

	
	\item Determine the vertical and horizontal asymptotes of the following functions
	\vspace{-0.4cm}
	\begin{multicols}{3}
	\[\mbox{(a) } y = f(x) = \frac{3x^2}{x^2-16} \]	
	
	\[\mbox{(b) } y = f(x) = \frac{3x^2}{x^2-9} \]
    
    \[\mbox{(c) } y = f(x)  = \frac{4x+3}{x-7} \]


    \end{multicols}
%=====================================================%
%% - Horizontal and Vertical Asymptotes
%% - http://media.wix.com/ugd/70b98b_39a909a40ea3098062c0bebfb4304ed6.pdf
	\item  Determine the vertical and horizontal asymptotes of the following functions.


		\vspace{-0.4cm}
	\begin{multicols}{3}
	\[\mbox{(a) } y = f(x) = \frac{2x^2}{x^2-16}\]	
	
	\[\mbox{(b) } y = f(x) = \frac{3x}{x+5}  \]
  	
    \[\mbox{(c) } y = f(x) = \frac{4x^2}{x^2-25} \]



    \end{multicols}
\item 
Consider the function $y = f(x) = x^4 - 6x^2 + 2$
\begin{enumerate}[(a)]
	\item Find the y intercept of f(x). 
	
	\item Find and classify the critical points of f(x) as local maxima or local minima or points of inflection. 
	
	\item Find all points of inflection. 
	
	\item Find the x values for which y = f(x) is concave up/down. 
	
	\item Determine the behaviour of y as $x \to +\infty$ and as $x \to -\infty$. 
	
	\item Sketch the graph of y = f(x) illustrating clearly the features of the curve obtained in parts (i – v). 
\end{enumerate}









\item The concentration of a drug in a patient's bloodstream 7 hours
after it was injected is given by
\[ A(h) = \frac{0.21h}{h^2 +4} \]

\begin{enumerate}[(a)]
	\item  Find the axis intercepts of $A(h)$.
	
	
	\item  Find and classify the critical points of $A(h)$ as local maxima or local minima.
	
	
	\item  Determine the behaviour of $A(h)$ as $h \rightarrow + \infty$.
	
	
	\item  Sketch the graph of $y = A(h)$ for $h \geq 0$ illustrating clearly
	the features of the curve obtained in parts (i - iii).
	
	
	
\end{enumerate}



\end{enumerate}
%======================================================== %
\end{document}
