%%- https://bookdown.org/kevin_davisross/probsim-book/linear-combinations-of-random-variables.html


\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\large

<span id="exm:unnamed-chunk-290" class="example"><strong>Example 5.33  </strong></span>
Recall the Colab activity where you simulated pairs of SAT Math ($ {\displaystyle X} $) and Reading ($ {\displaystyle Y} $) scores from Bivariate Normal distributions with different correlations. (See also Section <a href="sec-example-sat-both.html#sec-example-sat-both">3.9</a>.) 


You considered the distribution of the sum $ {\displaystyle T=X+Y} $ and difference $ {\displaystyle D= X - Y} $. Did changing the correction affect the <em>variance</em> of $ {\displaystyle T} $? Of $ {\displaystyle D} $?</p>

\subsection*{Variance of sums and differences of random variables.}

\begin{align*}
\textrm{Var}(X + Y) &amp; = \textrm{Var}(X) + \textrm{Var}(Y) + 2\textrm{Cov}(X, Y)\\
\textrm{Var}(X - Y) &amp; = \textrm{Var}(X) + \textrm{Var}(Y) - 2\textrm{Cov}(X, Y)
\end{align*}

\newpage
Assume that SAT Math ($ {\displaystyle X} $) and Reading ($ {\displaystyle Y} $) follow a Bivariate Normal distribution, Math scores have mean 527 and standard deviation 107, and Reading scores have mean 533 and standard deviation 100. Compute $ {\displaystyle \textrm{Var}(X + Y)} $ and $ {\displaystyle \textrm{SD}(X+Y)} $ for each of the following correlations.</p>

\begin{enumerate}[(a)]
\item $ {\displaystyle \textrm{Corr}(X, Y) = 0.77} $
\item $ {\displaystyle \textrm{Corr}(X, Y) = 0.40} $
\item $ {\displaystyle \textrm{Corr}(X, Y) = 0} $
\item $ {\displaystyle \textrm{Corr}(X, Y) = -0.77} $
\end{enumerate}

\subsection*{Solution}

\[ {\displaystyle \textrm{Cov}(X, Y) = \frac{\textrm{Corr}(X, Y)}{\textrm{SD}(X)\textrm{SD}(Y)} } \]
\begin{itemize}
\item $ {\displaystyle \textrm{Cov}(X, Y) = 0.77} $
\item $ {\displaystyle \textrm{Corr}(X, Y) = 0.40} $
\item $ {\displaystyle \textrm{Corr}(X, Y) = 0} $
\item $ {\displaystyle \textrm{Corr}(X, Y) = -0.77} $
\end{itemize}
%%%%%%%%%%%%%%%%%%%5
If $ {\displaystyle X} $ and $ {\displaystyle Y} $ have a positive correlation:</p>
\begin{itemize}
\item Large values of $ {\displaystyle X} $ are associated with large values of $ {\displaystyle Y} $ (so the sum is really large), and small values of $ {\displaystyle X} $ with small values of $ {\displaystyle Y} $ (so the sum is really small), so the sum exhibits more variability than it would if the values of $ {\displaystyle X} $ and $ {\displaystyle Y} $ were uncorrelated.
\item Large values of $ {\displaystyle X} $ are associated with large values of $ {\displaystyle Y} $ (so the difference is small), and small values of $ {\displaystyle X} $ with small values of $ {\displaystyle Y} $ (so the difference is small), so the difference exhibits less variability than it would if the values of $ {\displaystyle X} $ and $ {\displaystyle Y} $ were uncorrelated.
</ul>
If $ {\displaystyle X} $ and $ {\displaystyle Y} $ have a negative correlation:</p>
<ul>
\item Large values of $ {\displaystyle X} $ are associated with small values of $ {\displaystyle Y} $ (so the sum is moderate), and small values of $ {\displaystyle X} $ with large values of $ {\displaystyle Y} $ (so the sum is moderate), so the sum exhibits less variability than it would if the values of $ {\displaystyle X} $ and $ {\displaystyle Y} $ were uncorrelated.
\item Large values of $ {\displaystyle X} $ are associated with small values of $ {\displaystyle Y} $ (so the difference is large and positive), and small values of $ {\displaystyle X} $ with large values of $ {\displaystyle Y} $ (so the difference is large and negative), so the difference exhibits more variability than it would if the values of $ {\displaystyle X} $ and $ {\displaystyle Y} $ were uncorrelated.
\end{itemize}
The variance of the sum is the sum of the variances if and only if $ {\displaystyle X} $ and $ {\displaystyle Y} $ are uncorrelated.
\begin{equation}\begin{align*}
\textrm{Var}(X+Y)  = \textrm{Var}(X) + \textrm{Var}(Y)\qquad \text{if $X, Y$ are uncorrelated}\\
\textrm{Var}(X-Y)  = \textrm{Var}(X) + \textrm{Var}(Y)\qquad \text{if $X, Y$ are uncorrelated}
\end{align*}\end{equation}


\end{document}