\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{framed}
\usepackage{epsfig}
\usepackage{enumerate}
\usepackage{subfigure}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode"CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 201113:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{StatsResource} \rhead{Single Sample Procedures} \chead{Hypothesis Testing} %\input{tcilatex}

%% Single Sample Mean
\begin{document}
\large 
\noindent 
A random sample of twenty five bottles of a medicine that comes in liquid form is taken
and the contents of each bottle are accurately weighed. The sample mean weight (in
grams) of the contents of a bottle is 97.82 and the sample standard deviation is 0.64. You
may assume that the weights are Normally distributed.

\begin{enumerate}[(a)]
    \item Calculate a 95\% confidence interval for the underlying population mean
weight of medicine in a bottle.
\item Calculate a 95\% confidence interval for the underlying population variance of the weight of medicine in a bottle.
\item According to the manufacturer, the underlying mean weight of medicine in a
bottle is exactly 100 grams. It is suspected that the underlying mean weight of
medicine is in fact less than 100 grams. Perform an appropriate test of the
manufacturer's claim at the 5\% significance level, stating the null and
alternative hypotheses. Report your conclusions. 
\end{enumerate}
\newpage 
\subsection*{Solutions}
\end{document}
