

\subsection*{Question 11}
%%	 \textbf{MA4413 Autumn 2008 paper}

A model of an on-line computer system gives a mean times to retrieve a record from a direct access storage system device of 200 milliseconds, with a standard deviation of 58 milliseconds. 

If it can assumed that the retrieval times are normally distributed:

### Exercises 

A. What proportion of retrieval times will be greater than 75 milliseconds?

B. What proportion of retrieval times will be between 150 and 250 milliseconds?

C. What is the retrieval time below which 10% of retrieval times will be?
<p>


	
Let's tackle each exercise step by step, using the properties of the normal distribution.

### Given:
- Mean ($\mu$) = 200 milliseconds
- Standard deviation ($\sigma$) = 58 milliseconds

### A. Proportion of Retrieval Times Greater Than 75 Milliseconds
To find the proportion of retrieval times greater than 75 milliseconds, we need to calculate the z-score and then use the standard normal distribution table.

$$z = \frac{X - \mu}{\sigma} = \frac{75 - 200}{58} = \frac{-125}{58} \approx -2.16$$

Using the z-table, we find that the cumulative probability for $ z = -2.16 $ is approximately 0.0154. This is the probability that a retrieval time is less than 75 milliseconds.

Therefore, the proportion of retrieval times greater than 75 milliseconds is:
$$1 - P(X < 75) = 1 - 0.0154 = 0.9846$$

So, approximately **98.46%** of retrieval times will be greater than 75 milliseconds.

### B. Proportion of Retrieval Times Between 150 and 250 Milliseconds
We need to calculate the z-scores for both 150 and 250 milliseconds and then find the area between these z-scores.

For 150 milliseconds:
$$z_1 = \frac{150 - 200}{58} = \frac{-50}{58} \approx -0.86$$

For 250 milliseconds:
$$z_2 = \frac{250 - 200}{58} = \frac{50}{58} \approx 0.86$$

Using the z-table:
- The cumulative probability for $ z = -0.86 $ is approximately 0.1949.
- The cumulative probability for $ z = 0.86 $ is approximately 0.8051.

The proportion of retrieval times between 150 and 250 milliseconds is:
$$P(150 < X < 250) = P(X < 250) - P(X < 150) = 0.8051 - 0.1949 = 0.6102$$

So, approximately **61.02%** of retrieval times will be between 150 and 250 milliseconds.

### C. Retrieval Time Below Which 10% of Retrieval Times Will Be
We need to find the z-score corresponding to the 10th percentile, and then convert it back to the original scale using the mean and standard deviation.

Using the z-table, the z-score for the 10th percentile is approximately -1.28.

Now, convert the z-score to the original scale:
$$X = \mu + z \sigma = 200 + (-1.28) \times 58 \approx 200 - 74.24 = 125.76$$

So, the retrieval time below which 10% of retrieval times will be is approximately **125.76 milliseconds**.

Feel free to ask if you have any more questions or need further assistance!