
\subsection*{The Exponential distribution}
The average lifespan of a laptop is 5 year. You may assume that the lifespan of laptop computers follows an exponential distribution. Useful calculations are provided with each question.

### Exercises 
*  What is the probability that the lifespan of the laptop will be at least 6 years.
	$$e^{-6/5} = 0.3011942$$
<p>
*  What is the probability that the lifespan of the laptop will not exceed 4 years.
	$$e^{-4/5} = 0.449329$$
	---
*  What is the probability that the lifespan of the laptop will be between 5 years and 6 years.
	$$e^{-5/5} = 0.3678794$$
<p>

---


 \textbf{Important Formulae}

$$
P( X \geq k) = e^{-k \lambda }$$
---
$$
P( X \leq k) = 1 -e^{-k\lambda }$$

---

To solve these exercises, we use the exponential distribution. The probability density function (PDF) of an exponential distribution with parameter $\lambda$ is given by:
$$f(t; \lambda) = \lambda e^{-\lambda t}$$
where $ t $ is the time and $ \lambda $ is the rate parameter.

Given that the average lifespan of the laptop is 5 years, the rate parameter $\lambda$ is:
$$\lambda = \frac{1}{5} = 0.2$$

### Exercise Solutions

**1. What is the probability that the lifespan of the laptop will be at least 6 years?**

The probability that the lifespan $ T $ is at least 6 years is given by:
$$P(T \geq 6) = 1 - P(T < 6) = 1 - F(6)$$
where $ F(t) $ is the cumulative distribution function (CDF) of the exponential distribution:
$$F(t) = 1 - e^{-\lambda t}$$

So,
$$P(T \geq 6) = 1 - (1 - e^{-\lambda \cdot 6}) = e^{-6/5} \approx 0.3011942$$

Thus, the probability is **0.3012** (or 30.12%).

**2. What is the probability that the lifespan of the laptop will not exceed 4 years?**

The probability that the lifespan $ T $ does not exceed 4 years is given by the CDF $ F(4) $:
$$P(T \leq 4) = F(4) = 1 - e^{-4/5} \approx 1 - 0.449329 = 0.550671$$

Thus, the probability is **0.5507** (or 55.07%).

**3. What is the probability that the lifespan of the laptop will be between 5 years and 6 years?**

The probability that the lifespan $ T $ is between 5 years and 6 years is:
$$P(5 \leq T \leq 6) = F(6) - F(5)$$

So,
$$F(5) = 1 - e^{-5/5} = 1 - e^{-1} \approx 1 - 0.3678794 = 0.6321206$$
$$F(6) = 1 - e^{-6/5} \approx 0.6988058$$

Then,
$$P(5 \leq T \leq 6) = F(6) - F(5) = 0.6988058 - 0.6321206 = 0.0666852$$

Thus, the probability is **0.0667** (or 6.67%).

Feel free to ask if you have any more questions or need further assistance!

---

---	
