---
title: "Sum of Random Numbers from 1 to 5"
subtitle: "Random Variables"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    font_size: 20pts
    nature:
      highlightStyle: github
      countIncrementalSlides: false
---

<style type="text/css">
  body{
  font-size: 20pt;
}
</style>

```{r eval=FALSE,include=FALSE}

# CT6 
# - ASI 2005 April Question B - 1
# - ASI 2006 April Question B - 1

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(knitr)
library(dplyr)
library(janitor)


```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent_inverse(
  base_color = "#3C989E", #)(
#  base_color = "#1c5253",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "400", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

A computer chooses a number at random $n$ times from the set $\{1, 2, 3, 4, 5\}$ (with replacement).

Let $S$ denote the sum of the numbers chosen. 

#### Exercises

Show that $E(S) = 3n$ and $\textrm{Var}(S) = 2n$.


---

#### Solution

To calculate the expected value $E(S)$ and variance $\textrm{Var}(S)$ of the sum $S$, we'll use the ***linearity of expectation*** and the ***properties of the variance***.

**Expected Value E(S):**

* Let $X_i$ be the random variable representing the i-th number chosen. 
'
* Since the numbers are chosen with replacement, each $X_i$ is independently and identically distributed (IID) with the same probability mass function as the set ${1, 2, 3, 4, 5}$.

The expected value of each $X_i$ is given by:

$$E(X_i) = \frac{(1 + 2 + 3 + 4 + 5)}{5} = 3$$

---

Using the linearity of expectation, we can find the expected value of the sum $S$:

$$\begin{eqnarray} E(S) &=& E(X_1 + X_2 + ... + X_n) \\ & &\\ &=& E(X_1) + E(X_2) + ... + E(X_n) \\& &\\ &=& 3n\end{eqnarray}$$

Remark $E(X_1) = 3$, $E(X_2) = 3$ etc 

---

**Variance $\textrm{Var}(S)$:**

Since the $X_{i}$'s are IID, the variance of the sum $S$ is the sum of the individual variances:

$$\begin{eqnarray} \textrm{Var}(S) &=& \textrm{Var}(X_1 + X_2 \;+ \;...\; + X_n)\\& &\\&=& \textrm{Var}(X_1) + \textrm{Var}(X_2) \;+ \;...\; + \textrm{Var}(X_n)\end{eqnarray}$$

---

**Variance $\textrm{Var}(S)$:**


* To find the variance of each $X_i$, we can use the formula:

$$\textrm{Var}(X_{i}) = E(X_{i}^2) - (E(X_{i}))^2$$

* First, let's calculate $E(X_{i}^2)$:

$$E(X_{i}^2) = \frac{(1^2 + 2^2 + 3^2 + 4^2 + 5^2)}{ 5} = 11$$

* Now we can find $\textrm{Var}(X_{i})$:

$$\textrm{Var}(X_{i}) = 11 - 3^2 = 2$$


Finally, the variance of the sum $S$ is:

$$\textrm{Var}(S) = 2 + 2 + ... + 2\mbox{ (n times)} = 2n$$

---

#### Conclusion 

Therefore, we have shown that $\textrm{E}(S) = 3n$ and $\textrm{Var}(S) = 2n$.

---

BLANK

---


BLANK

---