
\documentclass[a4paper12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{enumerate}
\usepackage{multicol}
\usepackage{subfigure}
\usepackage{fancyhdr}
\usepackage{listings}
\usepackage{framed}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{chngpage}
%\usepackage{bigints}

\usepackage{vmargin}
% left top textwidth textheight headheight
% headsep footheight footskip
\setmargins{2.0cm}{2.5cm}{16 cm}{22cm}{0.5cm}{0cm}{1cm}{1cm}
\renewcommand{\baselinestretch}{1.3}

\setcounter{MaxMatrixCols}{10}

\begin{document}
\large 


%%- http://webpages.iust.ac.ir/matashbar/teaching/schaum_probability.pdf

%%-- PAge 287
%%-- 9.9



People arrive at a telephone booth according to a Poisson process at an average rate of 12 per 
hour, and the average time for each call is an exponential r.v. with mean 2 minutes. 

\begin{enumerate}[(a)]
    \item  What is the probability that an arriving customer will find the telephone booth occupied? 
\item It is the policy of the telephone company to install additional booths if customers wait an 
average of 3 or more minutes for the phone. Find the average arrival rate needed to justify a 
second booth. 
\end{enumerate}

\section*{Solution}
\begin{itemize}
    \item (a) The telephone service can be modeled as an M/M/1 queueing system with $\lambda = 1/5$, $\mu = 1/2$ and $\rho = \lambda / \mu = 2/5$.
\item The probability that an arriving customer will find the telephone occupied is $P(L > 0)$, where 
$L$ is the average number of customers in the system. 
\item Thus, from Eq. (9.1 3), 
\end{itemize}
\[P(L>0) = 1-p_{0} = 1-(1-\rho) = \rho = \frac{2}{5} = 0.4 \]
\begin{itemize}
    \item (b) From Eq. (9.1 7), 
    \[ W_{q} = \frac{\lambda}{\mu(\mu-\lambda)} = \frac{\lambda}{0.5(0.5-\lambda)} \geq 3\]
from which we obtain $\lambda \geq 0.3$ per minute.
\item Thus, the required average arrival rate to justify the second 
booth is 18 per hour.
\end{itemize}

 

\end{document}