
\item[(b)] \textbf{\textit{Inference Procedures (10 Marks)}}\\
Two IT training companies, \textit{XtraTech} and \textit{YourSkills}, offer an exam preparation course for a well-known computer industry certification. A study was carried out to compare the results from the most recent group of students from both companies.
\begin{itemize}
\item[$\bullet$]30 students from the \textit{XtraTech} course have completed the test. The average score for these students was 910 marks with a standard deviation of 48 marks.

\item[$\bullet$]25 students from the \textit{YourSkills} course have completed the test. Their average score was 950 marks with a standard deviation of 42 marks.
\end{itemize}

Test the hypothesis that the both sets of students perform equally well on average. You may use a significance level of 5\%. You may assume that both samples are normally distributed and have equal variance.
%\end{itemize}
\begin{itemize}
\item[(i)] (2 Marks) Formally state the null and alternative hypotheses for this procedure.
\item[(ii)] (2 Marks) Compute the point estimate for the difference in means of the results from both courses.
\item[(iii)] (2 Marks) Compute the appropriate value for standard error for this test. Clearly show your workings.
\item[(iv)] (2 Marks) Compute the test statistic.
\item[(v)] (2 Marks) What is your conclusion for this procedure?
\end{itemize}


\subsection*{Two sample mean}
\begin{itemize}
\item Hypotheses (brief written description required)
\[ H_0 :  \mu_1 = \mu_2\]
\[ H_1 :  \mu_1 \neq \mu_2\]
\item 
\item point estimate:  diffference in means (950-910=) 40 marks
\item Standard Error (from formulae)
\[\sqrt{\frac{s^2_1}{n_1} + \frac{s^2_2}{n_2} }\]
\item Critical Value = 1.96 (Large Sample.)
\end{itemize}

