\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{enumerate}
\usepackage{subfigure}
\usepackage{fancyhdr}
\usepackage{listings}
\usepackage{framed}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{chngpage}
%\usepackage{bigints}


\setcounter{MaxMatrixCols}{10}

\begin{document}


%====================================%
  \subsection*{Q2. Paired t-Test (11 Marks)}

The typing speeds for one group of eight IT students were recorded both at the beginning of year 1 of their studies and at the end of year 4. The results (in words per minute) are given below:
  
  \begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
Subject& A& B& C& D& E &F &G &H \\ \hline
Year 1 &173& 183& 176& 191& 184 &177& 175& 177\\ \hline
Year 4 &172 &184 &180 &190& 191& 187& 181& 183\\ \hline
\end{tabular}
\end{center}

%Calculate a 95\% confidence interval for the difference between the mean number of marks obtained by males and females in the population of school leavers as a whole.
%(7 marks)

A study was carried out to determine whether students improve in terms of typing speed over the four years of their university studies. A significance level of 5\% is used.\\
\bigskip
There are 11 questions listed below, with 1 mark awarded for each correct answer.
\begin{itemize}
\item[i.] Briefly explain the difference between paired samples and independent samples.
\item[ii.] Compute the case-wise differences.
\item[ii.] Compute the mean of the case-wise differences.
\item[iv.] Compute the standard deviation of the case-wise differences.
\item[v.] Formally state the null hypothesis.
%\item[v.] Formally state the alternative hypothesis.
\item[vi.] Formally state the alternative hypothesis.
\item[vii.] Compute the standard error for mean of case-wise differences.
\item[viii.] Compute the Test Statistic.
\item[ix.] What is the appropriate value for \textit{degrees of freedom}?.
\item[x.] What is the Critical Value?
  \item[xi.] Discuss your conclusion to this test, supporting your statement with reference to appropriate values.
\end{itemize}



\subsection*{Part (a)}

\begin{itemize}
\item
\item
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\subsection*{Part (b)}

\begin{itemize}
\item
\item
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\subsection*{Part (c)}

\begin{itemize}
\item
\item
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
