\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{enumerate}
\usepackage{subfigure}
\usepackage{fancyhdr}
\usepackage{listings}
\usepackage{framed}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{chngpage}
%\usepackage{bigints}


\setcounter{MaxMatrixCols}{10}

\begin{document}

 A 12-week plyometric-training programme was devised to improve standing long jump performance for track and field athletes.

A group of ten athletes are selected to take part. To test whether this training improves performance, the athletes are tested for their long jump performance
before they undertake a plyometric-training programme and then again at the end of the programme 
(i.e., the dependent variable is "standing long jump performance", and the two related groups are the standing long jump values "before" and "after" the 12-week plyometric-training programme).

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Thu Nov 02 12:44:35 2017
\begin{table}[ht]
\centering
\begin{tabular}{|r|r|r|}
\hline
& Before & After \\ 
\hline
1 & 225 & 239 \\ 
2 & 214 & 223 \\ 
3 & 211 & 221 \\ 
4 & 210 & 221 \\ 
5 & 203 & 217 \\ 
6 & 219 & 224 \\ 
7 & 200 & 214 \\ 
8 & 202 & 211 \\ 
9 & 224 & 226 \\ 
10 & 209 & 221 \\ 
\hline
\end{tabular}
\end{table}

\begin{enumerate}[(a)]
\item Briefly explain the difference between paired samples and independent samples.
\item Compute the mean of the case-wise differences.
\item Compute the standard deviation of the case-wise differences.
\item By performing a suitable hypothesis test, what is your conclusion about the effectiveness of this training program. 
\item Calculate a 95\% confidence interval for the mean of the case-wise differences.

\end{enumerate}


\end{document}




