\documentclass[]{article}
\usepackage{framed}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multicol}
%opening

\begin{document}

%---------------------------------------%
\section*{Question 4 (Sample Variant 1)[25 marks]}

\begin{itemize}
\item[(a)]
 \textbf{\textit{Theory of Statistical Inference  (9 Marks)}}\\ Answer the following questions on the theory of statistical inference.
\begin{itemize}
\item[(i)] (4 Marks) Briefly describe the central limit theorem.
\item[(ii)] (1 Mark) Provide a brief description of the standard error.
\item[(iii)] (2 Marks) In the context of hypothesis testing, explain what a p-value is, and how it is used. Support your answer with a simple example.
\item[(iv)] (2 Marks) What is meant by Type I error and Type II error?
\end{itemize}


\item[(b)] \textbf{\textit{Binary Classification (6 Marks)}}\\
For following binary classification outcome table, calculate the following appraisal metrics.
\begin{itemize}	
\item[(i)] (1 Mark)	Accuracy
\item[(ii)] (1 Mark)	Recall
\item[(iii)] (1 Mark)	Precision
\item[(iv)] (1 Mark)	F-measure
\end{itemize}	

\begin{center}
\begin{tabular}{|c|c|c|}
\hline  & \phantom{spa}Predict Negative\phantom{spa} & \phantom{spa}Predict Positive\phantom{spa} \\ 
\hline\phantom{spa} Observed Negative \phantom{spa}&	9530	&	10	\\ 
\hline \phantom{spa}Observed Positive\phantom{spa} & 	300	&	160	\\ 
\hline 
\end{tabular} 
\end{center}

\begin{itemize}	
\item[(v)] (2 Marks) Explain why the F-measure is considered a more informative measure of performance than the Accuracy score.
\end{itemize}

\bigskip
\item[(c)]  \textbf{\textit{Hypothesis Testing (9 Marks)}}\\
In a computer hardware manufacturing plant, machine X and machine Y produce identical components. The management investigate whether or not there is a difference in the mean diameter of the components from both machines.

\begin{itemize}
\item[$\bullet$] A random sample of 144 components from machine X had a mean of 36.38 mm and a standard deviation of 3.0 mm.
\item[$\bullet$] A random sample of 225 components from machine Y had a mean of 36.88 mm and a standard deviation of 2.8 mm.
\end{itemize}
A hypothesis test was used to determine whether or not the means are significantly different.
A $5\%$ significance level was used.

\begin{itemize}
\item[(i)] (2 Marks) What is the null and alternative hypothesis?
\item[(ii)] (4 Marks) Compute the test statistic.
\item[(iii)] (3 Marks) What is your conclusion for this procedure? Justify your answer.
\end{itemize}

\end{itemize}
\end{document}