
*  A die is thrown twice. A is the event that the sum is 7. B is the event that the first die roll results in a 1. C is the event that the second die roll results in a 6. 
i)Are the events A, B and C independent?
ii)Are the events A, B and C pairwise independent?
* A coin is tossed until it falls on the same side twice in a row.
--- 
\item[(i)] Define the set of elementary events of such an experiment.
\item[(ii)]  Calculate the probability that the coin is thrown exactly 5 times.
\item[(iii)]  Calculate the probability that the number of throws is even.

%--------------------------------------------------%
\itemIn a newspaper on average 1 in 10 000 characters is incorrectly printed. Suppose the paper contains 50 000 characters. Calculate the exact probability that 
 --- 
\item[(i)]no printing errors are made
\item[(ii)]at least 3 errors are made
 
Using the appropriate approximation, estimate these two probabilities. 




*  Suppose calls come into a call centre randomly at a rate of one per 30 seconds.
i) What is the distribution of the time to the second call?
ii) Using this distribution, calculate the probability that the second call arrives within a minute. 
iii) Using the appropriate discrete distribution, calculate the probability that at least 2 calls are received in a minute (note this probability has to be the same as above).
iv) What is the exact distribution of the time to the 200th call?
v) Using the central limit theorem, give the normal distribution which approximates the distribution from iv).
vi) Using your answer from v), estimate the probability that the time to the 200th call is less than 102 minutes.

