\section*{Probability Distributions}


--- 
* The discrete uniform distribution
* The continuous uniform distribution
* The binomial disribution
* The poisson distribution
* The exponential distribution
* the Normal distribution


%* uniform - The lower and upper bounds are 13cm and 21cm respectively.
%
%* A computer server breaks down, on average, once every three months.
--- 
* What is the probability that the server breaks down three times in a quarter?
* What is the probability that a server breaks down exactly five times in one year?


Assume that the number of weekly study hours for students at a certain university
is approximately normally distributed with a mean of 22 and a standard deviation
of 6.
--- 
* Find the probability that a randomly chosen student studies less than 12
hours.
* Estimate the percentage of students that study more than 37 hours.



%A charity believes that when it puts out an appeal for charitable donations the donations it receives 
%will normally distributed with a mean 50 and 
%
%standard deviation €6, and
%
% it is assumed that donations will be independent of each other.
%
%---  
%* Find the probability that the first donation it receives will be less than€40.
%
%* Compute the probability that it will be between €40and €45.
%* Compute the value $x$ such that 5\% of donations are more than €$x$.
%
%
In an examination the scores of students who attend schools of type A are
normally distributed about a mean of 55 with a standard deviation of 6. The
scores of students who attend type B schools are normally distributed about a
mean of 60 with a standard deviation of 5.
Which type of school would have a higher proportion of students with marks above 70?

The heights for a group of forty rowing club members are tabulated as follows;

\begin{table}[ht]
\begin{center}
\begin{tabular}{|rrrrrrrrrr|}

\hline
141 & 148 & 149 & 149 & 155 & 156 & 167 & 169 & 169 & 170 \\
171 & 173 & 175 & 176 & 177 & 179 & 182 & 182 & 183 & 183 \\
183 & 184 & 184 & 184 & 185 & 185 & 185 & 186 & 186 & 189 \\
191 & 191 & 191 & 191 & 192 & 192 & 192 & 193 & 194 & 199 \\
\hline
\end{tabular}
\end{center}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5555

\begin{enumerate}
* Summarize the data in the above table using a frequency table. Use 6 class intervals, with 140 as the lower limit of the first interval.
* Draw a histogram for the above data.
* Comment on the shape of the histogram. Based on the shape of the histogram, what is the best measure of centrality and variability?
* Construct a box plot for the above data. Clearly demonstrate how all of the necessary values were computed.
\end{enumerate}


