
* The following contingency table illustrates the number of 500 students in different
departments according to gender.

\begin{center}
\begin{tabular}{|c|c|c|c|}
  \hline
  % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
   & Computer Science & Engineering & Food Science \\\hline
  Males & 180 & 100 & 20  \\  \hline
  Females & 60 & 80 & 60  \\ \hline

  \hline
\end{tabular}
\end{center}

\begin{enumerate}[(i)]
*  What is the probability that a randomly chosen person from the sample is a
computer science student?
*  What is the probability that a randomly chosen person from the sample is both female and studying statistics?
% *  What is the probability that a randomly chosen person from the sample is male?
*  Given that a student studies statistics, what is the probability that the student is female?
%*  What is the probability that a randomly chosen person from the sample is a male or a statistics student?
% * (2 marks) Given that the student is female, what is the probability that she is an equine science student?
\end{enumerate}


    * 
An electronics assembly subcontractor receives its entire supply of resistors from two suppliers. Company A provides 65\% of the subcontractor's resistors, while company B supplies the remainder. The additional information has also been made available.
--- 
* 4\% of the resistors provided by company A failed the final test,
* 5\% of company B's resistors also fail the final test.

\noindent Answer the following questions:
\begin{enumerate}[(a)]
* What is the probability that a resistor fails the final test?
*  What is the probability that a resistor fails the final test given that the resistor in question came from company A?
*  What is the probability that a resistor that fails final test was supplied by company A?
\end{enumerate}
