---
title: "Cox Proportional Hazard Models"
subtitle: "Survival Analysis"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      countIncrementalSlides: false
---

```{r eval=FALSE,include=FALSE}

# CT6 
# - ASI 2005 April Question B - 1
# - ASI 2006 April Question B - 1

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(knitr)
library(dplyr)
library(janitor)


```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent_inverse(
  base_color = "#3C989E", #)(
#  base_color = "#1c5253",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```


A direct insurance sales office of a motor insurance company receives random number of enquiry calls every day. The number of calls each day follows a Poisson distribution with unknown mean $\beta$.
Prior beliefs about $\beta$ are specified by a Gamma distribution with mean of 200 and standard deviation of 50. The sales team has received 240 calls daily on average recently.

Calculate the Bayesian estimate of $\beta$ under Quadratic loss.

---

The Bayesian estimate of $\beta$ under Quadratic loss is given by the posterior mean.

---

**Step 1: Specify the likelihood function**

Given that the number of calls each day follows a Poisson distribution with mean $\beta$, the likelihood function for a single day is:

$$L(\beta|x) = \frac{e^{-\beta} \beta^x}{x!}$$

where $x$ is the observed number of calls on a given day.

---

**Step 2: Specify the prior distribution**

The prior distribution for $\beta$ is a Gamma distribution with mean 200 and standard deviation 50. 

The Gamma distribution has the following probability density function:

$$f(\beta) = \frac{\beta^{a-1} e^{-\beta/\theta}}{\theta^a \Gamma(a)}$$

where $a$ is the shape parameter and $\theta$ is the scale parameter.

We can find $a$ and $\theta$ from the given mean and standard deviation:

* Mean = $a\theta = 200$
* Variance = $a\theta^2 = 50^2 = 2500$

Solving these equations, we get $a = 16$ and $\theta = 12.5$.

---

**Step 3: Calculate the posterior distribution**

The posterior distribution is proportional to the product of the likelihood and the prior:

$$f(\beta|x) \propto L(\beta|x) f(\beta)$$

Substituting the likelihood and prior functions, we get:

$$f(\beta|x) \propto \frac{e^{-\beta} \beta^x}{x!} \cdot \frac{\beta^{15} e^{-\beta/12.5}}{12.5^{16} \Gamma(16)}$$

---

Simplifying, we get:

$$f(\beta|x) \propto \beta^{x+15} e^{-\beta(1+1/12.5)}$$

This is the kernel of a Gamma distribution with shape parameter $x+16$ and scale parameter $1/(1+1/12.5) = 12.5/13.5$.

---

**Step 4: Calculate the posterior mean**

The posterior mean is the Bayesian estimate of $\beta$ under Quadratic loss. 

For a Gamma distribution with shape parameter $a$ and scale parameter $\theta$, the mean is $a\theta$.

Therefore, the posterior mean is:

$$\hat{\beta} = (x+16) \cdot \frac{12.5}{13.5}$$

Substituting $x = 240$ (the average number of calls received daily), we get:

$$\hat{\beta} = (240+16) \cdot \frac{12.5}{13.5} \approx 231.48$$

Therefore, the Bayesian estimate of $\beta$ under Quadratic loss is approximately 231.48.


---
\noindent
A direct insurance sales office of a motor insurance company receives random number of enquiry calls every day. The number of calls each day follows a Poisson distribution with unknown mean $\beta$.
Prior beliefs about $\beta$ are specified by a Gamma distribution with mean of 200 and standard deviation of 50. The sales team has received 240 calls daily on average recently.


\noindent Calculate the Bayesian estimate of $\beta$ under Quadratic loss.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\noindent \textbf{Solution}

\begin{itemize}
    \item Let the prior distribution of $\beta$ be Gamma distribution with parameters α and λ.
   \item Dividing Mean by Variance;
,
Thus


   \item The posterior distribution of $\beta$ is then given by:
this is similar to the pdf of Gamma distribution with parameters
.
   \item Under quadratic loss, the Bayesian estimate is given by the mean of the posterior distribution, which is
=
= 237.03
\end{itemize}
