\documentclass[]{report}

\voffset=-1.5cm
\oddsidemargin=0.0cm
\textwidth = 480pt

\usepackage{framed}
\usepackage{subfiles}
\usepackage{graphics}
\usepackage{newlfont}
\usepackage{eurosym}
\usepackage{amsmath,amsthm,amsfonts}
\usepackage{amsmath}
\usepackage{color}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\begin{document}

\subsubsection{Worked Example Question 4}

The mean and standard deviation of the salaries of 16 Irish full-time workers are €5000  and €3000, respectively.

i)  Test the hypothesis that the mean salary of all Irish full-time workers is €4000 at a significance level of 5\%.   (6 marks)


\begin{description}
\item[Step 1 :] Formally state the null and alternative hypotheses
\item[Step 2 :] Determine the test statistic
\item[Step 3 :] Determine the critical value
\item[Step 4 :] Decision Rule
\end{description}



Given
\begin{itemize}
\item Observed value : Sample mean     x= 5000 
\item Null Value (Expected mean under null hypothesis)     o= 4000   
\item Population standard deviation is unknown.
\item Use sample standard deviation s = 3000 as an estimate.
\item Significance  = 0.05
\item Sample size n = 16  ( small sample)
\end{itemize}


\noindent \textbf{Hypotheses}
\begin{itemize}
\item[H0] $\mu=4000$    True mean salary is €4000
\item[Ha] $\mu \neq 4000$    True mean salary is  not €4000

\end{itemize}

\noindent \textbf{Test statistic}

Remember the general structure of a test statistic

\[TS =\frac{Observed Value-Null Value}{Std. Error} \]


\begin{itemize}
\item Standard ErrorS.E.(x) =sn=300016= 750

\item Test Statistic\[\frac{x-0}{S.E.(X)}=\frac{5000 -4 000}{750}= 1.33\]

\end{itemize}



\noindent \textbf{Critical values}
\begin{itemize}
\item The sample size (n=16) is small (n30). Use t distribution with n-1 degrees of Freedom.
\item The test is two tailed.  k= 2  ( "" symbol in the alternative hypothesis).
\item Column = k =0.052= 0.025
\end{itemize}

\textbf{Murdoch Barnes table 7}

\begin{itemize}
\item Row: df = 15         (n-1)
\item Column = 0.025
\item Critical value =  2.131 
\end{itemize}


\noindent \textbf{Decision rule}

\begin{framed}
\noindent Is the absolute value of the test statistic value greater than the critical value?
\begin{itemize}
\item If Yes: we reject the null hypothesis

\item If No: We fail to reject the null hypothesis. (not enough evidence)
\end{itemize}
\end{framed}

If No: We fail to reject the null hypothesis. (not enough evidence)


Here TS = 1.33  is not greater than CV = 2.131.


We fail to reject the null hypothesis. We can not rightly say that the mean salary is not €4000 per month.


ii)      What assumption is made in this testing procedure? Is this assumption reasonable?  (2 marks)

\begin{framed}
\begin{itemize}
\item The assumption made in this testing procedure is that salaries are normally distributed.
\item This is not a valid assumption as the distribution of salaries is known to be skewed (lots of low values, few high values).
\end{itemize}
\end{framed}


\end{document}
