\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{framed}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode"CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 201113:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{MS4222} \rhead{Kevin O'Brien} \chead{Binomial Distribution} %\input{tcilatex}
\begin{document}

\begin{itemize}
	\item Research was carried out on the number of flights leaving a particular airport last year. 
	
	\item Of 170 fights that departed on one particular day, 107 flights were to destinations within Europe. 
	\item Out of all these 170 flights, 36 departures were delayed. 
	
	\item Of the 36 delayed flights, 12 were to destinations outside Europe. 
	
	
\end{itemize}

%---------------------------------------- %



Assume that these numbers are representative of a typical 
day at this airport. Construct a frequency table and hence a probability table.\\ \bigskip
\textbf{Frequency Table}\\ \bigskip
\begin{tabular}{|c|c|c||c|}
	\hline  &  \phantom{sp} Europe \phantom{sp} & \phantom{sp} Outside \phantom{sp} &\phantom{sp} Total\phantom{sp}  \\ 
	\hline On Time  & 83 & 51 & 134 \\ 
	\hline Late & 24 & 12 & 36 \\ \hline
	\hline Total  & 107 & 63  & 170  \\ 
	\hline 
\end{tabular} 



%---------------------------------------- %




\textbf{Probability Table} \\ \bigskip
\begin{tabular}{|c|c|c||c|}
	\hline  &  \phantom{sp} Europe \phantom{sp} & \phantom{sp} Outside \phantom{sp} & \phantom{sp} Total\phantom{sp}  \\ 
	\hline On Time  & 48.82\% & 30.00\% & 78.82\% \\ 
	\hline Late & 14.12\% & 7.06\% &  21.18\% \\ \hline
	\hline Total  & 62.94\% & 30.06\% & 100.00\% \\ 
	\hline 
\end{tabular} 



Using the probability table answer the following questions. \\
\bigskip
For a randomly chosen flight departing from this airport, what is the probability that it: 
\begin{itemize}
	\item[(a)] Departs on time? 
	\item[(b)] Departs with a delay and is a flight outside Europe? 
	
	\item[(c)] Departs on time or is a flight outside Europe? 
	\item[(d)] Departs on time, given that you know it is a flight within Europe? 
	
	\item[(e)] Is a flight within Europe, given that you know that it departs on time?
\end{itemize}


%===========================================================================%
\subsection*{May 2013 Question 4 Probability}
\begin{center}
	\begin{tabular}{|c|c|c|c|}
		\hline  & within $W$ & outside $O$ & Totals \\ 
		\hline Correct time $C$ & 83 & 51 & 134 \\ 
		\hline Delayed $D$ & 24 & 12 & 36 \\ 
		\hline Totals & 107 & 63 & 170 \\ 
		\hline 
	\end{tabular} 
\end{center}\begin{itemize}
\item Probability of departing at correct time
\[P(C) = 107/170\]



\item Probability of being delayed and flying outside europe 
\[P(D  \mbox{ and } O) = 12/170\]
\item Probability of 
\[P() \]
\item Probability of 
\[P() \]
\item Probability of 
\[P() \]
\end{itemize}
%============================================================%


\end{document}
