\documentclass[]{report}

\voffset=-1.5cm
\oddsidemargin=0.0cm
\textwidth = 480pt

\usepackage{framed}
\usepackage{subfiles}
\usepackage{graphics}
\usepackage{newlfont}
\usepackage{eurosym}
\usepackage{enumerate}
\usepackage{amsmath,amsthm,amsfonts}
\usepackage{amsmath}
\usepackage{color}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\begin{document}



\section*{Small Sample Hypothesis Test: Worked Example}

\begin{itemize}

\item The manufacturer claims that average tube life for a particular brand of ultraviolet tube
is 9,000 hr. \item Test this claim at the 5 percent level of significance against the alternative hypothesis
that the mean life is not 9,000 hr \item We are given the following information:  a sample of $n = 10$ tubes the mean operating
life was $\bar{x} = 8,800$ hr. The sample standard deviation is be $s = 500$ hr.
%\item The standard deviation of the life for a particular brand of ultraviolet tube is known to
%\item Also it is assumed, but not known, that the operating life of the tubes is normally distributed.

%\item (Intuitively this would suggest a one-tailed test that the mean is less than 9000 hours)
\end{itemize}

\begin{framed}

\begin{itemize}
\item $H_0 \mbox{ : } $ $\mu = 9000$ (Average life span is 9000 hours.)
\item $H_1 \mbox{ : } $ $\mu \neq 9000$ (Average life span is not 9000 hours.)
\end{itemize}
\end{framed}
\bigskip
\begin{itemize}
\item The observed difference is -200 hours. (i.e. 8,800 - 9,000 hours)
\item The standard error is determined from formulae.
\[ S.E. (\bar{x}) = {s \over \sqrt{n}} = {500 \over \sqrt{10}}  = 158.1139 \]
\end{itemize}


%--------------------------------------------------------------------------------------%

\subsection*{Part (d): Test Statistic and Critical Value }

\[ TS = \frac{8800 - 9000}{158.11} \]
\begin{itemize}
\item The test statistic $TS = -1.265$
\item The CV is determined with $\alpha = 0.05$ and $k = 2$ (column = $\alpha/k=0.025$).
\item The sample is small n = 10 $df = n-1 = 9$ (i.e. row =9).
\item Therefore $CV = 2.262$

\item (Remark: If the sample was large, we could use $CV = 1.96$).

\end{itemize}


%--------------------------------------------------------------------------------------%

\subsection*{Part (d): Decision Rule }

\begin{itemize}
\item \textbf{Decision:}Is $|TS| >CV$? Is $1.265 > 2.262$?
\item No. We fail to reject the null hypothesis. \item There is not enough evidence to say that the mean lifespan is not 9000 hours.
\end{itemize}








%------------------------------------------------------------------------------%

\end{document}
