\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{framed}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode"CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 201113:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{MathsResource} \chead{Probability Distributions} \rhead{Poisson Distributions} %\input{tcilatex}
\begin{document}

\begin{enumerate}
    \item 
Cars enter a car wash at an average rate of 4 per half hour. 
\begin{enumerate}[(a)]
    \item Compute the probability that the 3 cars arrive in a half hour period.
\item Compute the probability that the 3 cars arrive in a 15 minute period.
\end{enumerate}

\item 
Consider an $M/M/1$ system with arrivals $X_a \sim \text{Poisson}(\lambda_a=3 \text{ / minute})$ and service time \\$T_s \sim \text{Exponential}(\lambda_s=4 \text{ / minute})$. Calculate the following:\\[-0.2cm]
\begin{itemize}
\item[(a)] The expected time spent in the system.  \item[(b)] The expected time spent in the queue component.  \item[(c)] The expected number of individuals in the system.   \item[(d)] The expected number of individuals in the queue component.  \item[(e)] The utilisation factor.  \item[(f)] The probability that an individual spends more than 2 minutes in the system.  \item[(g)] The probability that less than 3 individuals exit the system in a 1 minute period.
\end{itemize}


\item 
Assume that potholes arise on a road at a rate of  $\frac{1}{300}$ per metre according to a Poisson distribution. Calculate the following:\\[-0.2cm]

\begin{itemize}
\item[(a)] The probability that there are no potholes in 1km.  \item[(b)] The probability that there are at least 15 potholes in 6km.  \item[(c)] The probability that there are between 10 and 12 potholes in 3km.   \item[(d)] The value of $x$ such that $x$ or more potholes in 3km is approximately 10\%, i.e., $\Pr(X \ge x) \approx 0.1$.    \item[(e)] The probability that the next pothole appears within 100 metres.  \item[(f)] The probability that the next pothole is more than 1km away.  \item[(g)] The probability that the next pothole is between 300 and 1200 metres from here.   {\bf(h)} The average distance between potholes and the corresponding standard deviation.

\end{itemize}


\item
A life insurance salesman sells on the average 3 life insurance policies per week. Use Poisson's law to calculate the probability that in a given week he will sell

\begin{enumerate}[(a)]
\item some policies
\item 2 or more policies but less than 5 policies.
\item Assuming that there are 5 working days per week, what is the probability that in a given day he will sell one policy?
\end{enumerate}



\end{enumerate}
\end{document}

