\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{framed}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode"CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 201113:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{MathsResource} \chead{Probability} \rhead{Tutorial Sheets} %\input{tcilatex}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5555

\begin{enumerate}

%====================================================================================%


    \item 
Large and small bottles of water are manufactured in a factory. The volume of
water in the large bottles follows a Normal distribution with mean 1.5 litres and
standard deviation 0.01. The volume of water in the small bottles follows an
independent Normal distribution with mean 0.5 litres and standard deviation
0.008.
\begin{enumerate}[(a)]
\item  One large bottle and three small bottles are chosen at random. What is
the probability that the volume in the large bottle is greater than the
total volume in the three small bottles?
\item Find the distribution of the total volume of 10 large bottles and 3 small
bottles.
\end{enumerate}

%==================================================================================================%
\item
%%- RSS - HC2 - 2011 - Question 3
\begin{enumerate}[(a)]
In a certain large population, the heights X in cm of adult males have a Normal distribution with mean 170 and variance 100. 

\begin{enumerate}[(i)]
\item Find the probability that a randomly chosen man is within 5 cm of the population average height.  
\item Find the probability that a randomly chosen man is more than 185 cm tall.  
\item Given that a randomly chosen man is more than 185 cm tall, find the probability that he is more than 189.6 cm tall.  
\end{enumerate}

\item Four men are chosen at random from this population. 
\begin{enumerate}[(i)]
\item Find the probability that all four are within 5 cm of the population average height.  
\item Find the probability that exactly two of the four are within 5 cm of the population average height. 
\item Find the probability that the average height of the sample of four is within 5 cm of the population average height. 
\end{enumerate}

\item You are given that $P(X > 189.6) = 0.025$. Given a random sample of 100 men from the population, let Y denote the number of men in the sample who are over 189.6 cm tall. State 
\begin{enumerate}[(i)]
\item the exact distribution of Y, 
\item a suitable approximation to the exact distribution of Y. Use this approximate distribution to find the value of $P(Y > 3)$. 
\end{enumerate}


 

\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\item A manufacturer produces bags of sweets. The weights of the bags are
independently distributed with mean 30 g and standard deviation 5 g. A
random sample of 50 bags of sweets is taken.
\begin{enumerate}[(a)]
\item State the approximate distribution of the mean weight of the bags in the
sample, quoting any results you use.
\item Use this distribution to find the probability that the mean weight of the
bags in the sample is less than 29 g.
\item  Suppose instead a random sample of size n bags is taken. It is desired
that the probability that the mean weight of bags in the sample is below
29 g is less than 0.05. Find the minimum required value of n.
\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\item The random variables $X_i$, $i = \{1,\ldots, n\}$, are independent and are Normally distributed
with means $\mu_i$ and variances $\sigma^2_i$. 
Their total is given by
$T = \sum^{n}_{i=1}X_i$

\begin{enumerate}[(a)]
\item  Write down E(T).
\item  Write down Var(T).
\item  What is the distribution of T?
\end{enumerate}

\item  A company packs parcels of books. Suppose the weights of hardback books
are Normally distributed with mean 1.5 kg and standard deviation 0.5 kg and
the weights of paperback books are Normally distributed with mean 0.8 kg and
standard deviation 0.3 kg. Assume the weights are all independent of each
other.
\begin{enumerate}[(a)]
%--------------%
\item  A parcel has three hardback books and six paperback books. Find the
probability that the parcel weighs more than 11 kg.

\item  Find the probability that three hardback books weigh more than six
paperback books.
\item  A pallet of hardback books is to be moved by a fork-lift truck. Show
that the maximum number of books which can be put on the pallet, so
that there is a probability of no more than 0.01 that the combined
weight of the books exceeds 100 kg, is given by the largest integer $n$
that satisfies the inequality
$1.5n + 1.1632 \sqrt{n} - 100 < 0$.
\end{enumerate}
\end{enumerate}
\end{document}
