
\documentclass[]{article}
\usepackage{framed}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{graphicx}
%opening

\begin{document}

%---------------------------------------%
\section*{Question 2 (Sample Variant 2)[25 marks]}
\begin{itemize}

\item[(a)] \textbf{\textit{Probability Distribution (8 Marks)}}\\ % Exponential %6 MARKS
A computer software company which specializes in statistical software sells 4 software licences every day, on average. Answer the following questions.
    \begin{itemize}
    \item[i] (2 marks) What is the probability that the software company sells at least two licence in one particular day?
    \item[ii] (3 marks) What is the probability that the software company will sell exactly one licence in one particular day?
    \item[iii] (3 marks) What is the probability that the software company will sell sixteen licences or more in a five day working week?
    \end{itemize}


\item[(b)] \textbf{\textit{Normal Distribution (9 Marks)}}\\ % Exponential %6 MARKS
 A telecommunications company has determined that the number of products sold on a weekly basis is normally distributed with a mean of 900 and standard deviation of 40.
\begin{itemize}
\item[i] (3 Mark) Estimate the proportion of weeks will the company sell more than 960 products.

\item[ii] (3 Mark) Estimate the proportion of weeks will the company sell less more than 860 products.
\item[iii] (3 Mark) Estimate the proportion of weeks will there be sales of between 880
products and 960 products?
\end{itemize}

\item[(c)] \textbf{\textit{Probability Distribution (8 Marks)}}\\ % Exponential %6 MARKS

For a digital communication channel, the probability of a bit being received in error is $10\%$. Consider the case where 100 bits are transmitted. Answer the following questions.

\begin{itemize}
\item[i] (3 marks)	What is the probability that the number of bits received in error is 10?
\item[ii] (2 marks) What is the probability that the number of bits received in error is greater than 10?
\item[iii] (2 marks)	What is the probability that the number of bits received in error does not exceed 20?
\end{itemize}

\end{itemize}
\end{document}