

\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{framed}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode"CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 201113:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{StatsResource} \chead{Inference Procedures} \rhead{Hypothesis Testing} %\input{tcilatex}
\begin{document}

%-------------------------------------------------------------------------------------------%

\section*{Worked Example }
\begin{itemize}
\item For a random sample of 10 light bulbs, the mean bulb life is 4,000 hr with a standard deviation of 200 hours.
\item For another brand of bulbs whose useful life is also assumed to be normally distributed, a random sample of 8 has a sample mean of 4,300 hours
and a sample standard deviation of 250 hours. \item Test the hypothesis that there is no difference between the
mean operating life of the two brands of bulbs, using the 5 percent level of significance
\end{itemize}
\medskip 
%-------------------------------------------------------------------------------------------%


\subsection*{Key Values}
\begin{itemize}\item The sample sizes are $n_1 = 10$ and $n_2 = 8$. (Remark: Small Aggregate Sample)
\item Mean values: $\bar{x}_1 = 4000$, $\bar{x}_2 = 4,300 $ , therefore the parameter estimate is the difference in these means, i.e. $\bar{x}_2 - \bar{x}_1 = 300$ hours
\item We need the standard deviations of both samples to compute the standard error. These values are $s_1  = 200$, $s_2 = 250$ hours respectively.
\item Degrees of freedom: $n_1 + n_2 - 2 = 10 + 8 - 2 = 16$
\end{itemize}\medskip 
%-------------------------------------------------------------------------------------------%

\subsection*{Pooled variance estimate}

\[ s^2_p = \frac{(n_1 - 1)s^2_1  + (n_2 - 1)s^2_ 2}{n_1 + n_2 - 2 } = \frac{(9 \times 200^2 ) +( 7 \times 250^2) }{ 16 } = 49843.75 \]

\medskip 
%-------------------------------------------------------------------------------------------%

\subsection*{Computing the Standard Error}
\[ S.E(\bar{x}_1 - \bar{x}_2) = \sqrt{s^2_p \left({1\over n_1}+{1\over n_2} \right)}\]

\[ S.E(\bar{x}_1 - \bar{x}_2) = \sqrt{49843.75 \left({1\over 10}+{1\over 8} \right)}\]

\[ S.E(\bar{x}_1 - \bar{x}_2) = \sqrt{11214.84} = 105.9\]

\medskip 

%-------------------------------------------------------------------------------------------%

\subsection*{Test Statistic and Critical Value}
\begin{itemize}
\item The Test Statistic is \[ TS  = {(4000-4300) - 0 \over 105.9}  = -2.83 \]
\item The Critical Value is determined from Murdoch Barnes table 7 with $\alpha = 0.05$, $k=2$, $df = 16 $
\item The Critical Value is determined from R code with $\alpha = 0.05$, $k=2$, $df = 16 $ \texttt{qt(0.975,df=16)=  2.119905}
\item Our value for the Critical Value is $CV = 2.120$
\item We can now apply the decision rule : Is the absolute value of the Test Statistic greater than the Critical Value?
\item Is $2.83 > 2.12$? Yes We reject $H_0$. There is evidence of a difference in means.
\end{itemize}
\medskip 



\begin{framed}

$\alpha$ is distributed equally between upper and lower tails (i.e. designed for two-tailed tests.)
\begin{center}
\begin{tabular}{c|cc}
$\nu$ & & $\alpha = 0.05$ \\ \hline
8&...&2.3060\\ \hline
9&...&2.2622\\ \hline
10&...&2.2281\\ \hline
11&...&2.2010\\ \hline
12&...&2.1788\\ \hline
13&...&2.1604\\ \hline
14&...&2.1448\\ \hline
15&...&2.1314\\ \hline
16&...&2.1199\\ \hline
17&...&2.1098\\ \hline
18&...&2.1009\\ \hline
\end{tabular}
\end{center}
\end{framed}
\newpage 
\subsection*{Test Statistic and Critical Value}
\begin{itemize}

\item The Critical Value is determined using the following information: $\alpha = 0.05$, $k=2$, $df = 16 $ % \texttt{qt(0.975,df=16)=  2.119905}
\item Therefore $CV = 2.120$
\item We can now apply the decision rule : Is the absolute value of the Test Statistic greater than the Critical Value?
\begin{framed}
\textbf{Decision Rule}
\[ |TS| > CV ?  \]
\begin{itemize}
\item If Yes: Reject the null Hypothesis
\item If No : Fail to reject the Null Hypothesis
\end{itemize}
\end{framed}
\item Is $2.83 > 2.12$? Yes We reject $H_0$. There is evidence of a difference in means.
\end{itemize}
\newpage 
BLANK


\newpage 
BLANK





%---------------------------------------------------------%

\begin{itemize}
\item  Point estimate : $\bar{x} - \bar{y}$ = 1.469
\item  Standard Error: 0.5805
\[ S.E.(\bar{x}-\bar{y}) = \sqrt{\frac{2.743}{17} + \frac{2.985}{17}}  \]
\item  Quantile : 1.96 (Large sample, with confidence level of $95\%$.)
\end{itemize}

\[ 1.469  \pm (1.96 \times 0.5805) = (0.3321,2.607) \]

This analysis provides evidence that the mean consumption level per hour for X-cel is higher than the mean consumption level per hour for Yellow, and that the difference between means in the population is likely to be between 0.332 and 2.607 units.



\end{document}



%-------------------------------------------------------------------------------------------%

\textbf{Example 3: Difference in Means (e) }
\textbf{Test Statistic and Critical Value}\\
\begin{itemize}
\item The Test Statistic (usual structure) is \[ TS  = {(-300) - 0 \over 105.9}  = -2.83 \]
\item The Critical Value is determined  with $\alpha = 0.05$, $k=2$, $df = 16 $. 
\item From statistical tables: $CV = 2.120$
\item We can now apply the decision rule : Is the absolute value of the Test Statistic greater than the Critical Value?
\item Is $2.83 > 2.12$? Yes We reject $H_0$. There is evidence of a difference in means. 
\item There is enough evidence to suggest that there is a difference in lifespans for the two brands.
\end{itemize}







\end{document}


\end{document}
